%----------------------------------------------------
% Piazza
%----------------------------------------------------
\noindent \textbf {\Large \sc Additional Information for the Course}:

\vspace{1cm}

%----------------------------------------------------
\noindent \underline{Teaching Assistants (TA):}
%----------------------------------------------------

\noindent All TA Office Hours will take place in \textbf{KPTC 307} except where otherwise noted. Discussion Sections begin on Wednesday April 4th. Discussion Sections all take place on \textbf{Wednesdays from 3:30pm--4:20pm} and Students are assigned according to their Last Name.

\vspace{1cm}

\begin{tabular}{l l | l | l l }

TA Name & Email & Office Hours & Discussion & Last Names \\ \hline

Wen Han Chiu & \href{mailto:wenhan@uchicago.edu}{wenhan@} & Tues 4:30pm & KPTC 103 & A -- K \\


Kristian Mackewicz & \href{mailto:kmackewicz@uchicago.edu}{kmackewicz@} & Thur 2:30pm & KPTC 105 & L -- Z  \\


\end{tabular}

\vspace{1cm}

%----------------------------------------------------
\noindent \underline{Exams:}
%----------------------------------------------------
  
  \begin{itemize}
  
    \item There will be two exams, a mid-term given during the lecture period as scheduled in the syllabus and a final exam, as scheduled by the Registrar.
    \item The mid-term will be given on Monday, Apr. 30 during class.  The mid-term will count toward 25\% of your grade.
    \item The final exam will be given on Wednesday, June 6 from 10:30am--12:30pm. The final exam will count toward 30\% of the course grade.
    \item The exams will be closed book. For both exams, you will be given supplementary material with the exam. Calculators will be permitted for use during the exam. No other notes or references will be allowed.
    \item \textbf{\emph{There are no make-up exams}}. If there is an important reason that you cannot take an exam, make arrangements with the Prof. David Miller at least one day in advance of the exam. If you are sick or an emergency arises which prevents you from taking the exam without prior arrangement, you must have a signed note from your doctor or undergraduate advisor explaining your absence. No exceptions will be made to this rule and you will get a 0 grade for a missed exam if these conditions are not met.

  \end{itemize}  
  

\newpage  
%----------------------------------------------------
\noindent \underline{Schedule and Section Assignment Information:}
%----------------------------------------------------

  \begin{itemize}

    \item Discussion Sections will begin meeting in Week 2 of Spring Quarter.  Room assignments will be posted on the bulletin boards outside KPTC 106.

  \end{itemize}
  


%----------------------------------------------------
\noindent \underline{Piazza}
%----------------------------------------------------

\noindent This term we will be using \textbf{Piazza} for class discussion. The system is highly catered to getting you help fast and efficiently from classmates, the TA, and myself. 

\begin{itemize}

  \item Rather than emailing questions to the teaching staff, I encourage you to post your questions on Piazza. 

  \item If you have any problems or feedback, email myself or the Piazza developers: \href{mailto:team@piazza.com}{team@piazza.com}

  \item Find our class page at: \href{https://piazza.com/uchicago/spring2018/phys227/home}{https://piazza.com/uchicago/spring2018/phys227/home}
  
\end{itemize}  


%----------------------------------------------------
\noindent \underline{Miscellaneous}
%----------------------------------------------------

\begin{itemize}

  \item Students with special needs or who may need extra time on any exam or other deadlines should alert me during Week 1 or as soon as possible after enrolling in the course.
  
\end{itemize}  

